% http://pascal.inrialpes.fr/data2/grogez/CV/g-rogez_CV.pdf
% http://www.robots.ox.ac.uk/~aarnab/assets/CV_Anurag_Arnab.pdf
% https://thoth.inrialpes.fr/people/tlucas/cv_tlucas.pdf
% http://lear.inrialpes.fr/people/pluc/pauline_luc_cv.pdf

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Fabien Baradel} % Your name
\jobtitle{Research Scientist}
% \address{2 rue Dr Bally, 38000 Grenoble}
\address{
%        (+33)785706257 \\
        \href{fabien.baradel@naverlabs.com}{\textcolor{black}{fabien.baradel@naverlabs.com}} \\
        \href{https://fabienbaradel.github.io/}{\textcolor{black}{fabienbaradel.github.io}}
        }

\begin{document}

% \begin{rSection}{Summary}
%         I am a soon-to-graduate PhD candidate in Computer Vision and Machine Learning.
%         I am looking for industrial research positions for solving real word problems as well 
% \end{rSection}

\begin{rSection}{Education}
     \begin{rSubsection}{INSA Lyon}{Lyon, France}{PhD in Computer Vision \& Machine Learning}{October 2019 - June 2020}
            \item Thesis: "Structured deep learning for video analysis" advised by Christian Wolf and Julien Mille.
    \end{rSubsection}
    \begin{rSubsection}{ENSAI}{Rennes, France}{MSc in Statistics, "Diplôme d'ingénieur"}{2013 - 2016}
            \item Major in data science, suma cum laude (top of class), high honors.
            \item Erasmus semester at University of Warkwick, UK.
            \item BEng in Applied Economics at University of Paris Dauphine, France (double degree agreement).
    \end{rSubsection}
    \begin{rSubsection}{University of Grenoble Alps}{Grenoble, France}{BSc in Applied Mathematics}{2010 - 2013}
            \item Suma cum laude (top of class), high honors.
    \end{rSubsection}
\end{rSection}

\begin{rSection}{Work Experience}
    \begin{rSubsection}{NAVER LABS Europe}{Grenoble, France}{Research Scientist}{September 2020 - present}
                \item Conducting research in computer vision and machine learning in the CV team.
    \end{rSubsection}
     \begin{rSubsection}{INSA Lyon - LIRIS}{Lyon, France}{Doctoral Researcher}{October 2016 - June 2020}
                \item Conducting research on deep learning methods for computer vision.
                \item Publishing in top-tier conferences on topics related to human action understanding and causal reasoning.
                \item Integration of research methods into robotic platform.
                % \item Animation of weekly reading group meeting.
                \item Animation of weekly reading group meeting. \& co-supervision of master student interns.
                \item Active collaboration with Natalia Neverova (Research Scientist at Facebook AI Research).
     \end{rSubsection}
     \begin{rSubsection}{Google}{Grenoble, France}{Student Researcher}{April 2019 - March 2020}
            \item Worked on self-supervised learning from unlabelled video data with Cordelia Schmid and Chen Sun.
    \end{rSubsection}
    \begin{rSubsection}{Xerox Research Europe Center}{Grenoble, France}{Research Intern}{March 2016 - September 2016}
            \item Worked on unsupervised domain adaptation advised by Boris Chidlovskii and Gabriela Csurka.
    \end{rSubsection}
    \begin{rSubsection}{LICIT - IFSTTAR}{Lyon, France}{Research Intern}{Summer 2015}
            \item Developed a machine learning method for road traffic forecasting supervised by Romain Billot.
    \end{rSubsection}
\end{rSection}

\begin{rSection}{Academic visits}
     \begin{rSubsection}{Simon Fraser University}{Vancouver, Canada}{Vision \& Media Lab with Greg Mori}{February 2018 - June 2018}
            \item Worked on video classification from a human-object interactions perspective.
    \end{rSubsection}
     \begin{rSubsection}{University of Guelph}{Guelph, Canada}{Machine Learning Research Group with Graham Taylor}{Summer 2017}
            \item Developed an attention-based method for recognizing fine-grained human actions.
    \end{rSubsection}
\end{rSection}

%\newpage

\begin{rSection}{Publications \& Patents}
        \vspace{-1em}
        \item \href{https://arxiv.org/abs/1906.05743}{\textbf{Learning Video Representations using Contrastive Bidirectional Transformer}} \\
        \textit{Chen Sun, \textbf{Fabien Baradel}, Kevin Murphy and Cordelia Schmid.} \\ Under review, arXiv preprint:1906.05743, 2020. \vspace{0.3em}
        \item \href{https://openreview.net/forum?id=SkeyppEFvS}{\textbf{CoPhy: Counterfactual Learning of Physical Dynamics}} \\ \textit{\textbf{Fabien Baradel}, Natalia Neverova, Julien Mille, Greg Mori and Christian Wolf.} \\In Internattonal Conference in Representation Learning (ICLR), 2020. \textbf{(spotlight presentation)} \vspace{0.3em}
        \item \href{https://arxiv.org/abs/1806.06157}{\textbf{Object Level Visual Reasoning in Videos}} \\ \textit{\textbf{Fabien Baradel}, Natalia Neverova, Christian Wolf, Julien Mille and Greg Mori} \\ In IEEE European Conference on Computer Vision (ECCV), 2018. \vspace{0.3em}
        \item \href{https://hal.inria.fr/hal-01828083}{\textbf{Human Activity Recognition with Pose-driven Attention to RGB}} \\ \textit{\textbf{Fabien Baradel}, Christian Wolf and Julien Mille} \\ In British Machine Vision Conference (BMVC), 2018.
        \item \href{https://arxiv.org/abs/1802.07898}{\textbf{Glimpse Clouds: Human Activity Recognition from Unstructured Feature Points}} \\ \textit{\textbf{Fabien Baradel}, Christian Wolf, Julien Mille and Graham Taylor} \\ In IEEE Computer Vision and Patter Recognition (CVPR), 2018. \vspace{0.3em}
        \item \href{https://arxiv.org/abs/1712.08002}{\textbf{Human Action Recognition: Pose-based Attention draws focus to Hands}} \\ \textit{\textbf{Fabien Baradel}, Christian Wolf and Julien Mille} \\ In IEEE International Conference on Computer Vision (ICCV), Workshop "Hands in Action", 2017. \vspace{0.3em}
        \item \href{http://openaccess.thecvf.com/content_ICCV_2017_workshops/w38/html/Csurka_Discrepancy-Based_Networks_for_ICCV_2017_paper.html}{\textbf{Discrepancy-based networks for unsupervised domain adaptation: a comparative study}} \\ \textit{Gabriela Csurka, \textbf{Fabien Baradel}, Boris Chidlovskii and Stéphane Clinchant} \\ In IEEE Internat. Conf. on Comp. Vision (ICCV), Workshop "Task-CV", 2017. \vspace{0.3em}
	\item \href{https://patentscope.wipo.int/search/en/detail.jsf;jsessionid=3A48BFD50DA5C2E7D2DBD17E0B5F8D40.wapp2nB?docId=US225503247&recNum=21861&office=&queryString=&prevFilter=&sortOption=Pub+Date+Desc&maxRec=70863381}{\textbf{Conditional adaptation network for image classification}} \\ \textit{\textbf{Fabien Baradel}, Boris Chidlovskii and Gabriela Csurka} \\ US Patent - 15450620, 2017. \vspace{0.3em}
\end{rSection}

\begin{rSection}{Teaching experience}
        \begin{rSubsection}{Science-U}{Lyon, France}{Lecturer}{2018 - 2019}
               \item "Introduction to machine leaning", MSc Computer Science, 30h
       \end{rSubsection}
       \begin{rSubsection}{University Lyon 1}{Lyon, France}{Teaching Assistant}{Fall 2017}
               \item "Regression modeling" - MSc Data Science - TP 12h
               \item "Probability \& Statistics", BSc Computer Science \& Maths, TP 20h
       \end{rSubsection}
       \begin{rSubsection}{EPITA}{Lyon, France}{Lecturer}{Fall 2017}
               \item "Mathematics", Undergraduates, 24h
       \end{rSubsection}
       \begin{rSubsection}{ENSAI}{Rennes, France}{External Speaker}{January 2017}
               \item "Introduction to deep learning with tensorflow", MSc Data Science, 6h
       \end{rSubsection}
\end{rSection}

%\newpage

\begin{rSection}{Talks}
        \vspace{-1em}
        \item \textbf{Counterfactual learning for physical dynamics} \\ Invited talk at ICML 2020 workshop Object-Oriented Perception, Reasoning, and Causality. \hfill \textit{July 2020}
        \item \textbf{Visual reasoning in videos} \\ GDR ISIS-IA on Reasoning from Visual Signal. \hfill \textit{October 2018}
        \item \textbf{Pose and attention for action recogniton} \\ GDR ISIS on Pose and Gesture. \hfill \textit{December 2017}
\end{rSection}

\begin{rSection}{Miscellaneous}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{1ex}} l }
        Press coverage \ & \href{CVPR Daily 2018}{CVPR Daily 2018}. \\
        Reviewer \ & ECCV 2020, CVPR 2019-2020, ICCV 2019, ICML 2019, FG 2019, NIPS 2018, IJCV. \\
        Summer schools  \ &  DLRLSS 2017, PAISS 2019.\\
        Programming \ & Python, PyTorch, Tensorflow, R, Java, latex, git, bash. \\
        Github \ & \href{https://github.com/fabienbaradel}{\textcolor{black}{github.com/fabienbaradel}} \\
        Languages \ & French (native), English (professional proficiency). \\
        Sports \ & Ski-touring, hiking, triathlon.
\end{tabular}
\end{rSection}

\end{document}
